---
title: "Milestone 6"
author: "Miroslav Bergam"
date: "4/04/2020"
output: bookdown::pdf_document2
bibliography: bibliography.bib
link_citations: true
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = FALSE, warning = FALSE)

#### Load libraries
library(rio)
library(car)
library(dplyr)
library(Hmisc)
library(psych)
library(lavaan)
library(lattice)
library(corrplot)
library(broom)
library(gridExtra)
library(tidyverse)
library(randomForest)

#### Load custom function for mode
getmode <- function(v) {
  uniqv <- unique(v)
  uniqv[which.max(tabulate(match(v, uniqv)))]
}

```


So far, I've been able to replicate all 7 figures used in my main paper. I am still working on making the spacing and size of the graphs perfect so that they are readable (I ran into this issue with  I am able to produce the content of the 5 tables of the graph but I am running into bugs when I try to visualize them in stargazer or other programs. 


^[[All analysis for this paper is availible at https://github.com/mirobergam/milestone-5](https://github.com/mirobergam/milestone-6)]

### Figure 1

```{r}

### Load data; set the working directory to the folder that contains the downloaded files
dat <- rio::import("mturk_w2.csv")

### Make Figure 1
mfq.correlations <- c(cor(dat$Q197[!is.na(dat$Q197) & !is.na(dat$Wave2_Q197)], dat$Wave2_Q197[!is.na(dat$Q197) & !is.na(dat$Wave2_Q197)]),
                      cor(dat$Q53_21[!is.na(dat$Wave2_Q53_21)], dat$Wave2_Q53_21[!is.na(dat$Q53_21) & !is.na(dat$Wave2_Q53_21)]),
                      cor(dat$Q53_23[!is.na(dat$Wave2_Q53_23)], dat$Wave2_Q53_23[!is.na(dat$Q53_23) & !is.na(dat$Wave2_Q53_23)]),
                      cor(dat$Q53_24[!is.na(dat$Wave2_Q53_24)], dat$Wave2_Q53_24[!is.na(dat$Q53_24) & !is.na(dat$Wave2_Q53_24)]),
                      cor(dat$Q53_30[!is.na(dat$Wave2_Q53_30)], dat$Wave2_Q53_30[!is.na(dat$Q53_30) & !is.na(dat$Wave2_Q53_30)]),
                      cor(dat$Q53_31[!is.na(dat$Wave2_Q53_31)], dat$Wave2_Q53_31[!is.na(dat$Q53_31) & !is.na(dat$Wave2_Q53_31)]),
                      cor(dat$Q53_33[!is.na(dat$Wave2_Q53_33)], dat$Wave2_Q53_33[!is.na(dat$Q53_33) & !is.na(dat$Wave2_Q53_33)]),
                      cor(dat$Q53_20[!is.na(dat$Wave2_Q53_20)], dat$Wave2_Q53_20[!is.na(dat$Q53_20) & !is.na(dat$Wave2_Q53_20)]),
                      cor(dat$Q53_22[!is.na(dat$Wave2_Q53_22)], dat$Wave2_Q53_22[!is.na(dat$Q53_22) & !is.na(dat$Wave2_Q53_22)]),
                      cor(dat$Q53_26[!is.na(dat$Wave2_Q53_26)], dat$Wave2_Q53_26[!is.na(dat$Q53_26) & !is.na(dat$Wave2_Q53_26)]),
                      cor(dat$Q53_27[!is.na(dat$Wave2_Q53_27)], dat$Wave2_Q53_27[!is.na(dat$Q53_27) & !is.na(dat$Wave2_Q53_27)]),
                      cor(dat$Q53_28[!is.na(dat$Wave2_Q53_28)], dat$Wave2_Q53_28[!is.na(dat$Q53_28) & !is.na(dat$Wave2_Q53_28)]),
                      cor(dat$Q53_29[!is.na(dat$Wave2_Q53_29)], dat$Wave2_Q53_29[!is.na(dat$Q53_29) & !is.na(dat$Wave2_Q53_29)]),
                      cor(dat$Q53_32[!is.na(dat$Wave2_Q53_32)], dat$Wave2_Q53_32[!is.na(dat$Q53_32) & !is.na(dat$Wave2_Q53_32)]),
                      cor(dat$Q53_34[!is.na(dat$Wave2_Q53_34)], dat$Wave2_Q53_34[!is.na(dat$Q53_34) & !is.na(dat$Wave2_Q53_34)]),
                      cor(dat$Q53_35[!is.na(dat$Wave2_Q53_35)], dat$Wave2_Q53_35[!is.na(dat$Q53_35) & !is.na(dat$Wave2_Q53_35)]),
                      cor(dat$Q54_36[!is.na(dat$Wave2_Q54_36)], dat$Wave2_Q54_36[!is.na(dat$Q54_36) & !is.na(dat$Wave2_Q54_36)]),
                      cor(dat$Q54_37[!is.na(dat$Wave2_Q54_37)], dat$Wave2_Q54_37[!is.na(dat$Q54_37) & !is.na(dat$Wave2_Q54_37)]),
                      cor(dat$Q54_38[!is.na(dat$Wave2_Q54_38)], dat$Wave2_Q54_38[!is.na(dat$Q54_38) & !is.na(dat$Wave2_Q54_38)]),
                      cor(dat$Q54_39[!is.na(dat$Wave2_Q54_39)], dat$Wave2_Q54_39[!is.na(dat$Q54_39) & !is.na(dat$Wave2_Q54_39)]),
                      cor(dat$Q54_40[!is.na(dat$Wave2_Q54_40)], dat$Wave2_Q54_40[!is.na(dat$Q54_40) & !is.na(dat$Wave2_Q54_40)]),
                      cor(dat$Q54_42[!is.na(dat$Wave2_Q54_42)], dat$Wave2_Q54_42[!is.na(dat$Q54_42) & !is.na(dat$Wave2_Q54_42)]),
                      cor(dat$Q54_43[!is.na(dat$Wave2_Q54_43)], dat$Wave2_Q54_43[!is.na(dat$Q54_43) & !is.na(dat$Wave2_Q54_43)]),
                      cor(dat$Q54_44[!is.na(dat$Wave2_Q54_44)], dat$Wave2_Q54_44[!is.na(dat$Q54_44) & !is.na(dat$Wave2_Q54_44)]),
                      cor(dat$Q54_45[!is.na(dat$Wave2_Q54_45)], dat$Wave2_Q54_45[!is.na(dat$Q54_45) & !is.na(dat$Wave2_Q54_45)]),
                      cor(dat$Q54_46[!is.na(dat$Wave2_Q54_46)], dat$Wave2_Q54_46[!is.na(dat$Q54_46) & !is.na(dat$Wave2_Q54_46)]),
                      cor(dat$Q54_47[!is.na(dat$Wave2_Q54_47)], dat$Wave2_Q54_47[!is.na(dat$Q54_47) & !is.na(dat$Wave2_Q54_47)]),
                      cor(dat$Q54_48[!is.na(dat$Wave2_Q54_48)], dat$Wave2_Q54_48[!is.na(dat$Q54_48) & !is.na(dat$Wave2_Q54_48)]),
                      cor(dat$Q54_49[!is.na(dat$Wave2_Q54_49)], dat$Wave2_Q54_49[!is.na(dat$Q54_49) & !is.na(dat$Wave2_Q54_49)]),
                      cor(dat$Q54_50[!is.na(dat$Wave2_Q54_50)], dat$Wave2_Q54_50[!is.na(dat$Q54_50) & !is.na(dat$Wave2_Q54_50)]),
                      cor(dat$Q54_51[!is.na(dat$Wave2_Q54_51)], dat$Wave2_Q54_51[!is.na(dat$Q54_51) & !is.na(dat$Wave2_Q54_51)]))

mfq.correlations.labels <- c(
  "Political Ideology",
  "Whether or not some people were treated differently than others.",
  "Whether or not someone showed a lack of respect for authority.",
  "Whether or not someone violated standards of purity and decency.",
  "Whether or not someone did something disgusting.",
  "Whether or not someone was cruel.",
  "Whether or not someone showed a lack of loyalty.",
  "Whether or not someone suffered emotionally.",
  "Whether or not someone’s action showed love for his or her country.",
  "Whether or not someone cared for someone weak or vulnerable.",
  "Whether or not someone acted unfairly.",
  "Whether or not someone did something to betray his or her group.",
  "Whether or not someone conformed to the traditions of society.",
  "Whether or not someone was denied his or her rights.",
  "Whether or not an action caused chaos or disorder.",
  "Whether or not someone acted in a way that God would approve of.",
  "Compassion for those who are suffering is the most crucial virtue.",
  "When the government makes laws, the number one principle should be ensuring that everyone is treated fairly.",
  "I am proud of my country’s history.",
  "Respect for authority is something all children need to learn.",
  "People should not do things that are disgusting, even if no one is harmed.",
  "One of the worst things a person could do is hurt a defenseless animal.",
  "Justice is the most important requirement for a society.",
  "People should be loyal to their family members, even when they have done something wrong.",
  "Men and women each have different roles to play in society.",
  "I would call some acts wrong on the grounds that they are unnatural.",
  "It can never be right to kill a human being.",
  "I think it’s morally wrong that rich children inherit a lot of money while poor children inherit nothing.",
  "It is more important to be a team player than to express oneself.",
  "If I were a soldier and disagreed with my commanding officer’s orders, I would obey anyway because that is my duty.",
  "Chastity is an important and valuable virtue."
)

mfq.colors.labels <- c("#444444", rep("#000000", 6), rep("#444444", 24))

#tiff(height = 625, width = 1000, file = "fig1.tiff", pointsize = 15)

dotchart(rev(mfq.correlations), labels = rev(mfq.correlations.labels), 
         main = "Moral Factor Between-Wave Correlations (MTurk Data)", 
         gcolor = rev(mfq.colors.labels), color = rev(mfq.colors.labels), pch = 19, cex = 0.6)

#dev.off()
rm(dat)

```

### Figure 2

```{r}

dat <- rio::import("mturk_w3.csv")

### Make Figure 2
dat.cor <- dat %>% 
  select(
    ideology1,
    ideology2,
    ideology3,
    binding1,
    binding2,
    binding3,
    auth1,
    auth2,
    auth3,
    loyalty1,
    loyalty2,
    loyalty3,
    purity1,
    purity2,
    purity3,
    individualizing1,
    individualizing2,
    individualizing3,
    fair1,
    fair2,
    fair3,
    harm1,
    harm2,
    harm3
  )

var <- c(
  "Ideology (W1)", "Ideology (W2)", "Ideology (W3)",
  "Binding (W1)", "Binding (W2)", "Binding (W3)",
  "Authority (W1)", "Authority (W2)", "Authority (W3)",
  "Loyalty (W1)", "Loyalty (W2)", "Loyalty (W3)",
  "Purity (W1)", "Purity (W2)", "Purity (W3)",
  "Individualizing (W1)", "Individualizing (W2)", "Individualizing (W3)",
  "Fairness (W1)", "Fairness (W2)", "Fairness (W3)",
  "Harm (W1)", "Harm (W2)", "Harm (W3)"
)
colnames(dat.cor) <- var

vars <- c("Ideology (W1/W2)", "Binding (W1/W2)", "Authority (W1/W2)", "Loyalty (W1/W2)", "Purity (W1/W2)",
          "Fairness (W1/W2)", "Harm (W1/W2)", "Individualizing (W1/W2)" )
correlations <- c(
  cor(dat.cor$`Ideology (W1)`, dat.cor$`Ideology (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Binding (W1)`, dat.cor$`Binding (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Authority (W1)`, dat.cor$`Authority (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Loyalty (W1)`, dat.cor$`Loyalty (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Purity (W1)`, dat.cor$`Purity (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Individualizing (W1)`, dat.cor$`Individualizing (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Fairness (W1)`, dat.cor$`Fairness (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Harm (W1)`, dat.cor$`Harm (W2)`, method = c("pearson"), use = "pairwise.complete.obs")
)
correlations <- round(correlations, 3)
correlation.matrix <- cbind(vars, correlations)
#correlation.matrix

vars.2 <- c("Ideology (W1/W3)", "Binding (W1/W3)", "Authority (W1/W3)", "Loyalty (W1/W3)", "Purity (W1/W3)",
            "Fairness (W1/W3)", "Harm (W1/W3)", "Individualizing (W1/W3)" )
correlations.2 <- c(
  cor(dat.cor$`Ideology (W1)`, dat.cor$`Ideology (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Binding (W1)`, dat.cor$`Binding (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Authority (W1)`, dat.cor$`Authority (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Loyalty (W1)`, dat.cor$`Loyalty (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Purity (W1)`, dat.cor$`Purity (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Individualizing (W1)`, dat.cor$`Individualizing (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Fairness (W1)`, dat.cor$`Fairness (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Harm (W1)`, dat.cor$`Harm (W3)`, method = c("pearson"), use = "pairwise.complete.obs")
)
correlations.2 <- round(correlations, 3)
correlation.matrix.2 <- cbind(vars, correlations.2)
#correlation.matrix.2

vars.w3 <- c("Ideology (W2/W3)", "Binding (W2/W3)", "Authority (W2/W3)", "Loyalty (W2/W3)", "Purity (W2/W3)",
             "Fairness (W2/W3)", "Harm (W2/W3)", "Individualizing (W2/W3)" )
correlations.w3 <- c(
  cor(dat.cor$`Ideology (W2)`, dat.cor$`Ideology (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Binding (W2)`, dat.cor$`Binding (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Authority (W2)`, dat.cor$`Authority (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Loyalty (W2)`, dat.cor$`Loyalty (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Purity (W2)`, dat.cor$`Purity (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Fairness (W2)`, dat.cor$`Fairness (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Harm (W2)`, dat.cor$`Harm (W3)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Individualizing (W2)`, dat.cor$`Individualizing (W3)`, method = c("pearson"), use = "pairwise.complete.obs")
)
correlations.w3 <- round(correlations.w3, 3)
correlation.matrix.w3 <- cbind(vars.w3, correlations.w3)
#correlation.matrix.w3

#png(height = 1200, width = 800, file = "fig2.png")
#par(mfrow = c(3, 1))
dotchart(rev(correlations), labels = rev(vars), main = "", pch = 19, cex = 1.25)
dotchart(rev(correlations.2), labels = rev(vars.2), main = "", pch = 19, cex = 1.25)
dotchart(rev(correlations.w3), labels = rev(vars.w3), main = "", pch = 19, cex = 1.25)
#dev.off()
rm(dat)

```

### Figure 3

```{r}

### Load data; set the working directory to the folder that contains the downloaded files
dat <- rio::import("smithetal.csv")

### Make Figure 3
dat.cor <- dat %>% 
  select(
    def_w1,
    def_w2,
    econ_w1,
    econ_w2,
    soc_w1,
    soc_w2,
    EG1_BINDING_SHORT,
    EG2_BINDING_SHORT,
    authority1,
    authority2,
    loyalty1,
    loyalty2,
    purity1,
    purity2,
    EG1_IND_SHORT,
    EG2_IND_SHORT,
    fairness1,
    fairness2,
    harm1,
    harm2
  )

var_eg <- c(
  "Defense Ideology (W1)", "Defense Ideology (W2)",
  "Economic Ideology (W1)", "Economic Ideology (W2)",
  "Social Ideology (W1)", "Social Ideology (W2)",
  "Binding (W1)", "Binding (W2)",
  "Authority (W1)", "Authority (W2)",
  "Loyalty (W1)", "Loyalty (W2)",
  "Purity (W1)", "Purity (W2)",
  "Individualizing (W1)", "Individualizing (W2)",
  "Fairness (W1)", "Fairness (W2)",
  "Harm (W1)", "Harm (W2)"
)
colnames(dat.cor) <- var_eg

eg_vars <- c("Defense Ideology", "Economic Ideology", "Social Ideology", "Binding", "Authority", "Loyalty", "Purity", "Individualizing", "Fairness", "Harm")
eg_correlations <- c(
  cor(dat.cor$`Defense Ideology (W1)`, dat.cor$`Defense Ideology (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Economic Ideology (W1)`, dat.cor$`Economic Ideology (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Social Ideology (W1)`, dat.cor$`Social Ideology (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Binding (W1)`, dat.cor$`Binding (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Authority (W1)`, dat.cor$`Authority (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Loyalty (W1)`, dat.cor$`Loyalty (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Purity (W1)`, dat.cor$`Purity (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Individualizing (W1)`, dat.cor$`Individualizing (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Fairness (W1)`, dat.cor$`Fairness (W2)`, method = c("pearson"), use = "pairwise.complete.obs"),
  cor(dat.cor$`Harm (W1)`, dat.cor$`Harm (W2)`, method = c("pearson"), use = "pairwise.complete.obs")
)
eg_correlations <- round(eg_correlations, 3)
eg_correlation.matrix <- cbind(eg_vars, eg_correlations)
#eg_correlation.matrix
#png(height = 600, width = 800, file = "fig3.png")
dotchart(rev(eg_correlations), labels = rev(eg_vars), main = "Moral Factor Between-Wave Correlations (Smith et al Data)", pch = 19, cex = 1.25)
#dev.off()

rm(dat)

```

### Figure 4

```{r}

#### Set seed
set.seed(06011986)

### Load data; set the working directory to the folder that contains the downloaded files
dat <- rio::import("mturk_w3.csv")

### Make Figure 4
#png(height = 600, width = 800, file = "fig4.png")
par(mfrow = c(3, 3))
temp <- randomForest(ideology3 ~ ideology1 + ideology2 + binding1 + binding2 + binding3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Political Ideology", 
           labels = rev(c("Ideology (W1)", "Ideology (W2)", "Binding (W3)", "Binding (W2)", "Binding (W1)")), pch = 19)
temp <- randomForest(ideology3 ~ ideology1 + ideology2 + auth1 + auth2 + auth3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Political Ideology", 
           labels = rev(c("Ideology (W1)", "Ideology (W2)", "Authority (W3)", "Authority (W2)", "Authority (W1)")), pch = 19)
temp <- randomForest(ideology3 ~ ideology1 + ideology2 + loyalty1 + loyalty2 + loyalty3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Political Ideology", 
           labels = rev(c("Ideology (W1)", "Ideology (W2)", "Loyalty (W3)", "Loyalty (W2)", "Loyalty (W1)")), pch = 19)
temp <- randomForest(ideology3 ~ ideology1 + ideology2 + purity1 + purity2 + purity3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Political Ideology", 
           labels = rev(c("Ideology (W2)", "Ideology (W1)", "Purity (W2)", "Purity (W3)", "Purity (W1)")), pch = 19)
temp <- randomForest(ideology3 ~ ideology1 + ideology2 + individualizing1 + individualizing2 + individualizing3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Political Ideology", 
           labels = rev(c("Ideology (W1)", "Ideology (W2)", "Individualizing (W2)", "Individualizing (W3)", "Individualizing (W1)")), pch = 19)
temp <- randomForest(ideology3 ~ ideology1 + ideology2 + fair1 + fair2 + fair3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Political Ideology", 
           labels = rev(c("Ideology (W1)", "Ideology (W2)", "Fairness (W3)", "Fairness (W2)", "Fairness (W1)")), pch = 19)
temp <- randomForest(ideology3 ~ ideology1 + ideology2 + harm1 + harm2 + harm3, data = dat, na.action = na.omit, importance = TRUE, ntree =250)
varImpPlot(temp, type = 1, main = "Political Ideology", 
           labels = rev(c("Ideology (W1)", "Ideology (W2)", "Harm (W1)", "Harm (W2)", "Harm (W3)")), pch = 19)
#dev.off()

rm(dat)

```

### Figure 5

```{r}

#### Set seed
set.seed(06011986)

### Load data; set the working directory to the folder that contains the downloaded files
dat <- rio::import("mturk_w3.csv")

### Make Figure 5
par(mfrow = c(3, 3))
temp <- randomForest(binding3 ~ binding1 + binding2 + ideology1 + ideology2 + ideology3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Binding", 
           labels = rev(c("Binding (W2)", "Binding (W1)", "Political Ideology (W2)", "Political Ideology (W3)", "Political Ideology (W1)")), pch = 19)
temp <- randomForest(auth3 ~ auth1 + auth2 + ideology1 + ideology2 + ideology3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Authority", 
           labels = rev(c("Authority (W2)", "Authority (W1)", "Political Ideology (W2)", "Political Ideology (W3)", "Political Ideology (W1)")), pch = 19)
temp <- randomForest(loyalty3 ~ loyalty1 + loyalty2 + ideology1 + ideology2 + ideology3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Loyalty", 
           labels = rev(c("Loyalty (W2)", "Loyalty (W1)", "Political Ideology (W3)", "Political Ideology (W2)", "Political Ideology (W1)")), pch = 19)
temp <- randomForest(purity3 ~ purity1 + purity2 + ideology1 + ideology2 + ideology3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Purity", 
           labels = rev(c("Purity (W2)", "Purity (W1)", "Political Ideology (W2)", "Political Ideology (W1)", "Political Ideology (W3)")), pch = 19)
temp <- randomForest(individualizing3 ~ individualizing1 + individualizing2 + ideology1 + ideology2 + ideology3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Individualizing", 
           labels = rev(c("Individualizing (W2)", "Individualizing (W1)", "Political Ideology (W3)", "Political Ideology (W2)", "Political Ideology (W1)")), pch = 19)
temp <- randomForest(fair3 ~ fair1 + fair2 + ideology1 + ideology2 + ideology3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Fairness", 
           labels = rev(c("Fairness (W2)", "Fairness (W1)", "Political Ideology (W3)", "Political Ideology (W2)", "Political Ideology (W1)")), pch = 19)
temp <- randomForest(harm3 ~ harm1 + harm2 + ideology1 + ideology2 + ideology3, data = dat, na.action = na.omit, importance = TRUE, ntree = 250)
varImpPlot(temp, type = 1, main = "Harm", 
           labels = rev(c("Harm (W2)", "Harm (W1)", "Political Ideology (W2)", "Political Ideology (W1)", "Political Ideology (W3)")), pch = 19)
#dev.off()

rm(dat)

```

### Figure 6

```{r}

#### Set seed
set.seed(06011986)

### Load data; set the working directory to the folder that contains the downloaded files
dat <- rio::import("smithetal.csv")

### Make Figure 7
#png(height = 900, width = 800, file = "fig6.png")
par(mfrow = c(3, 2))
temp <- randomForest(def_w2 ~ EG2_BINDING_SHORT + def_w1 + EG1_BINDING_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Defense Ideology", 
           labels = rev(c("Defense Ideology (W1)", "Binding (W1)", "Binding (W2)")), pch = 19, lcolor = "#8a114e")
temp <- randomForest(def_w2 ~ EG2_IND_SHORT + def_w1 + EG1_IND_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Defense Ideology", 
           labels = rev(c("Defense Ideology (W1)", "Individualizing (W2)", "Individualizing (W1)")), pch = 19, lcolor = "#8a114e")
temp <- randomForest(econ_w2 ~ EG2_BINDING_SHORT + econ_w1 + EG1_BINDING_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Economic Ideology", 
           labels = rev(c("Economic Ideology (W1)", "Binding (W1)", "Binding (W2)")), pch = 19, lcolor = "#8a114e")
temp <- randomForest(econ_w2 ~ EG2_IND_SHORT + econ_w1 + EG1_IND_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Economic Ideology", 
           labels = rev(c("Economic Ideology (W1)", "Individualizing (W1)", "Individualizing (W2)")), pch = 19, lcolor = "#8a114e")
temp <- randomForest(soc_w2 ~ EG2_BINDING_SHORT + soc_w1 + EG1_BINDING_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Social Ideology", 
           labels = rev(c("Social Ideology (W1)", "Binding (W2)", "Binding (W1)")), pch = 19, lcolor = "#8a114e")
temp <- randomForest(soc_w2 ~ EG2_IND_SHORT + soc_w1 + EG1_IND_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Social Ideology", 
           labels = rev(c("Social Ideology (W1)", "Individualizing (W2)", "Individualizing (W1)")), pch = 19, lcolor = "#8a114e")
#dev.off()

rm(dat)

```

### Figure 7 

```{r}

#### Set seed
set.seed(06011986)

### Load data; set the working directory to the folder that contains the downloaded files
dat <- rio::import("smithetal.csv")

### Make Figure 7
#png(height = 500, width = 900, file = "fig7.png")
par(mfrow = c(2, 3))
temp <- randomForest(EG2_BINDING_SHORT ~ def_w2 + def_w1 + EG1_BINDING_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Binding", 
           labels = rev(c("Binding (W1)", "Defense Ideology (W2)", "Defense Ideology (W1)")), pch = 19, lcolor = "#8a114e")
temp <- randomForest(EG2_BINDING_SHORT ~ econ_w2 + econ_w1 + EG1_BINDING_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Binding", 
           labels = rev(c("Binding (W1)", "Economic Ideology (W2)", "Economic Ideology (W1)")), pch = 19, lcolor = "#8a114e")
temp <- randomForest(EG2_BINDING_SHORT ~ soc_w2 + soc_w1 + EG1_BINDING_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Binding", 
           labels = rev(c("Binding (W1)", "Social Ideology (W1)", "Social Ideology (W2)")), pch = 19, lcolor = "#8a114e")
temp <- randomForest(EG2_IND_SHORT ~ def_w2 + def_w1 + EG1_IND_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Individualizing", 
           labels = rev(c("Individualizing (W1)", "Defense Ideology (W1)", "Defense Ideology (W2)")), pch = 19, lcolor = "#8a114e")
temp <- randomForest(EG2_IND_SHORT ~ econ_w2 + econ_w1 + EG1_IND_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Individualizing", 
           labels = rev(c("Individualizing (W1)", "Economic Ideology (W2)", "Economic Ideology (W1)")), pch = 19, lcolor = "#8a114e")
temp <- randomForest(EG2_IND_SHORT ~ soc_w2 + soc_w1 + EG1_IND_SHORT, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Individualizing", 
           labels = rev(c("Individualizing (W1)", "Social Ideology (W2)", "Social Ideology (W1)")), pch = 19, lcolor = "#8a114e")
#dev.off()

rm(dat)

```

### Figure 8

```{r}

#### Set seed
set.seed(06011986)

### Load data; set the working directory to the folder that contains the downloaded files
dat <- rio::import("anes.csv")

### Make Figure 8
#png(height = 600, width = 700, file = "fig8.png")
par(mfrow = c(3, 3))
temp <- randomForest(ideow11 ~ binding + ideow6, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Ideology (W11)", 
           labels = rev(c("Ideology (W6)", "Binding (W7)")), pch = 19, lcolor = "#FFE519")
temp <- randomForest(ideow11 ~ authority + ideow6, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Ideology (W11)", 
           labels = rev(c("Ideology (W6)", "Authority (W7)")), pch = 19, lcolor = "#FFE519")
temp <- randomForest(ideow11 ~ ingroup + ideow6, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Ideology (W11)", 
           labels = rev(c("Ideology (W6)", "Loyalty (W7)")), pch = 19, lcolor = "#FFE519")
temp <- randomForest(ideow11 ~ purity + ideow6, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Ideology (W11)", 
           labels = rev(c("Ideology (W6)", "Purity (W7)")), pch = 19, lcolor = "#FFE519")
temp <- randomForest(ideow11 ~ individualizing + ideow6, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Ideology (W11)", 
           labels = rev(c("Ideology (W6)", "Individualizing (W7)")), pch = 19, lcolor = "#FFE519")
temp <- randomForest(ideow11 ~ fairness + ideow6, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Ideology (W11)", 
           labels = rev(c("Ideology (W6)", "Fairness (W7)")), pch = 19, lcolor = "#FFE519")
temp <- randomForest(ideow11 ~ harm + ideow6, data = dat, na.action = na.omit, importance=TRUE, ntree=250)
varImpPlot(temp, type = 1, main = "Ideology (W11)", 
           labels = rev(c("Ideology (W6)", "Harm (W7)")), pch = 19, lcolor = "#FFE519")
#dev.off()

rm(dat)

```

### Bibliography

@main_paper @side_paper_1 @side_paper_2 @side_paper_3 @side_paper_4

